The Unicode Cookbook \linebreak for Linguists

### 2018-08-09 book/chapters/implementation.tex
change bash explanation

<<eval=FALSE, tidy=FALSE, engine='bash'>>=
# get the paths to the R executables in bash
pathT=`Rscript -e 'cat(system.file("exec/tokenize", package="qlcData"))'`
pathW=`Rscript -e 'cat(system.file("exec/writeprofile", package="qlcData"))'`
@

<<eval=FALSE, tidy=FALSE, engine='bash'>>=
# make softlinks to the R executables in /usr/local/bin
sudo ln -is $pathT $pathW /usr/local/bin
@

>>>>

<<eval=FALSE, tidy=FALSE, engine='bash'>>=
pathT=`Rscript -e 'cat(system.file("exec/tokenize", package="qlcData"))'`
pathW=`Rscript -e 'cat(system.file("exec/writeprofile", package="qlcData"))'`
@

Then you can make softlinks to the R executables in \texttt{/usr/local/bin} by using the following command in the terminal:

<<eval=FALSE, tidy=FALSE, engine='bash'>>=
sudo ln -is $pathT $pathW /usr/local/bin
@

### 2018-08-09 book/main.tex
change bash explanation

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\noindent
\ttfamily
\hlstd{}\hlslc{\#\ get\ the\ paths\ to\ the\ R\ executables\ in\ bash}\hspace*{\fill}\\
\hlstd{pathT}\hlopt{=}\hlstd{}\hlstr{`Rscript\ {-}e\ 'cat(system.file("exec/tokenize",\ package="qlcData"))'`}\hlstd{}\hspace*{\fill}\\
\hlstd{pathW}\hlopt{=}\hlstd{}\hlstr{`Rscript\ {-}e\ 'cat(system.file("exec/writeprofile",\ package="qlcData"))'`}\hlstd{}\hspace*{\fill}
\mbox{}
\normalfont
\end{kframe}
\end{knitrout}

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\noindent
\ttfamily
\hlstd{}\hlslc{\#\ make\ softlinks\ to\ the\ R\ executables\ in\ /usr/local/bin}\hspace*{\fill}\\
\hlstd{sudo\ }\hlkwc{ln\ }\hlstd{}\hlkwb{{-}is\ }\hlstd{}\hlkwd{\$pathT\ \$pathW\ }\hlstd{}\hlopt{/}\hlstd{usr}\hlopt{/}\hlstd{local}\hlopt{/}\hlstd{bin}\hspace*{\fill}
\mbox{}
\normalfont
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{# link executables from within R}
\hlkwd{file.symlink}\hlstd{(}\hlkwd{system.file}\hlstd{(}\hlstr{"exec/tokenize"}\hlstd{,} \hlkwc{package} \hlstd{=} \hlstr{"qlcData"}\hlstd{),} \hlstr{"/usr/local/bin"}\hlstd{)}
\hlkwd{file.symlink}\hlstd{(}\hlkwd{system.file}\hlstd{(}\hlstr{"exec/writeprofile"}\hlstd{,} \hlkwc{package} \hlstd{=} \hlstr{"qlcData"}\hlstd{),} \hlstr{"/usr/local/bin"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(test} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"AABB"}\hlstd{,} \hlstr{"AАBВ"}\hlstd{))}
\end{alltt}
\begin{verbatim}
## [1] "AABB" "AАBВ"
\end{verbatim}
\begin{alltt}
\hlkwd{write.profile}\hlstd{(test)}
\end{alltt}
\begin{verbatim}
##   Grapheme Frequency Codepoint                UnicodeName
## 1        A         3    U+0041     LATIN CAPITAL LETTER A
## 2        B         3    U+0042     LATIN CAPITAL LETTER B
## 3        А         1    U+0410  CYRILLIC CAPITAL LETTER A
## 4        В         1    U+0412 CYRILLIC CAPITAL LETTER VE
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{example} \hlkwb{<-} \hlstr{"ÙÚÛÙÚÛ"}
\hlstd{profile_1} \hlkwb{<-} \hlkwd{write.profile}\hlstd{(example)}
\end{alltt}
\end{kframe}
\end{knitrout}

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:27 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Gr. & Freq. & Codepoint & Unicode Name \\ 
  \midrule
Ú & 1 & U+00DA & LATIN CAPITAL LETTER U WITH ACUTE \\ 
  Ú & 1 & U+0055, U+0301 & LATIN CAPITAL LETTER U, COMBINING ACUTE ACCENT \\ 
  Ù & 1 & U+00D9 & LATIN CAPITAL LETTER U WITH GRAVE \\ 
  Ù & 1 & U+0055, U+0300 & LATIN CAPITAL LETTER U, COMBINING GRAVE ACCENT \\ 
  Û & 1 & U+00DB & LATIN CAPITAL LETTER U WITH CIRCUMFLEX \\ 
  Û & 1 & U+0055, U+0302 & LATIN CAPITAL LETTER U, COMBINING CIRCUMFLEX ACCENT \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 1 (default settings, splitting grapheme clusters)} 
\label{tab:profile1}
\end{table}

@@

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & Unicode Name \\ 
  \midrule
́ & 1 & U+0301 & COMBINING ACUTE ACCENT \\ 
  ̀ & 1 & U+0300 & COMBINING GRAVE ACCENT \\ 
  ̂ & 1 & U+0302 & COMBINING CIRCUMFLEX ACCENT \\ 
  U & 3 & U+0055 & LATIN CAPITAL LETTER U \\ 
  Ú & 1 & U+00DA & LATIN CAPITAL LETTER U WITH ACUTE \\ 
  Ù & 1 & U+00D9 & LATIN CAPITAL LETTER U WITH GRAVE \\ 
  Û & 1 & U+00DB & LATIN CAPITAL LETTER U WITH CIRCUMFLEX \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 2 (splitting by code points)} 
\label{tab:profile2}
\end{table}

@@

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & Unicode Name \\ 
  \midrule
Ú & 2 & U+00DA & LATIN CAPITAL LETTER U WITH ACUTE \\ 
  Ù & 2 & U+00D9 & LATIN CAPITAL LETTER U WITH GRAVE \\ 
  Û & 2 & U+00DB & LATIN CAPITAL LETTER U WITH CIRCUMFLEX \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 3 (splitting by NFC code points)} 
\label{tab:profile3}
\end{table}

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & Unicode Name \\ 
  \midrule
́ & 2 & U+0301 & COMBINING ACUTE ACCENT \\ 
  ̀ & 2 & U+0300 & COMBINING GRAVE ACCENT \\ 
  ̂ & 2 & U+0302 & COMBINING CIRCUMFLEX ACCENT \\ 
  U & 6 & U+0055 & LATIN CAPITAL LETTER U \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 4 (splitting by NFD code points)} 
\label{tab:profile4}
\end{table}

@@

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Gr. & Freq. & Codepoint & Unicode Name \\ 
  \midrule
Ú & 2 & U+0055, U+0301 & LATIN CAPITAL LETTER U, COMBINING ACUTE ACCENT \\ 
  Ù & 2 & U+0055, U+0300 & LATIN CAPITAL LETTER U, COMBINING GRAVE ACCENT \\ 
  Û & 2 & U+0055, U+0302 & LATIN CAPITAL LETTER U, COMBINING CIRCUMFLEX ACCENT \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 5 (splitting by graphemes after NFD)} 
\label{tab:profile5}
\end{table}

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Gr. & Freq. & Codepoint & Unicode Name \\ 
  \midrule
Ú & 2 & U+00DA & LATIN CAPITAL LETTER U WITH ACUTE \\ 
  Ù & 2 & U+00D9 & LATIN CAPITAL LETTER U WITH GRAVE \\ 
  Û & 2 & U+00DB & LATIN CAPITAL LETTER U WITH CIRCUMFLEX \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 6 (splitting by graphemes after NFC)} 
\label{tab:profile6}
\end{table}

@@

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & UnicodeName \\ 
  \midrule
sh &  &  &  \\ 
  ch &  &  &  \\ 
  sch &  &  &  \\ 
  ie &  &  &  \\ 
  oo &  &  &  \\ 
  a & 2 & U+0061 & LATIN SMALL LETTER A \\ 
  c & 2 & U+0063 & LATIN SMALL LETTER C \\ 
  e & 3 & U+0065 & LATIN SMALL LETTER E \\ 
  f & 1 & U+0066 & LATIN SMALL LETTER F \\ 
  h & 4 & U+0068 & LATIN SMALL LETTER H \\ 
  i & 3 & U+0069 & LATIN SMALL LETTER I \\ 
  m & 4 & U+006D & LATIN SMALL LETTER M \\ 
  o & 2 & U+006F & LATIN SMALL LETTER O \\ 
  p & 2 & U+0070 & LATIN SMALL LETTER P \\ 
  s & 4 & U+0073 & LATIN SMALL LETTER S \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Manually edited profile skeleton} 
\label{tab:profile_skeleton1}
\end{table}

@@

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{lllll}
  \toprule
Left & Grapheme & Frequency & Codepoint & UnicodeName \\ 
  \midrule
mi & s &  &  &  \\ 
   & sh &  &  &  \\ 
   & ch &  &  &  \\ 
   & sch &  &  &  \\ 
   & ie &  &  &  \\ 
   & oo &  &  &  \\ 
   & a & 2 & U+0061 & LATIN SMALL LETTER A \\ 
   & c & 2 & U+0063 & LATIN SMALL LETTER C \\ 
   & e & 3 & U+0065 & LATIN SMALL LETTER E \\ 
   & f & 1 & U+0066 & LATIN SMALL LETTER F \\ 
   & h & 4 & U+0068 & LATIN SMALL LETTER H \\ 
   & i & 3 & U+0069 & LATIN SMALL LETTER I \\ 
   & m & 4 & U+006D & LATIN SMALL LETTER M \\ 
   & o & 2 & U+006F & LATIN SMALL LETTER O \\ 
   & p & 2 & U+0070 & LATIN SMALL LETTER P \\ 
   & s & 4 & U+0073 & LATIN SMALL LETTER S \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Orthography profile with contextual specification for <s>} 
\label{tab:profile_skeleton2}
\end{table}

@@

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{lllll}
  \toprule
Left & Grapheme & Right & Class & Replacement \\ 
  \midrule
 & a &  &  & a \\ 
   & c &  &  & c \\ 
   & e &  &  & e \\ 
   & i &  &  & i \\ 
   & n &  &  & n \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Orthography profile with empty columns for editing contexts} 
\label{tab:profile_editing_1}
\end{table}

@@

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{lllll}
  \toprule
Left & Grapheme & Right & Class & IPA \\ 
  \midrule
 & c & [ie] &  & tʃ \\ 
   & a &  &  & a \\ 
   & n &  &  & n \\ 
   & c &  &  & k \\ 
   & e &  &  & e \\ 
   & i &  &  & i \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Orthography profile with regex as context} 
\label{tab:profile_editing_2}
\end{table}

@@

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Aug  6 15:29:28 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{lllll}
  \toprule
Left & Grapheme & Right & Class & IPA \\ 
  \midrule
 & c & Vfront &  & tʃ \\ 
   & a &  &  & a \\ 
   & n &  &  & n \\ 
   & c &  &  & k \\ 
   & e &  & Vfront & e \\ 
   & i &  & Vfront & i \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Orthography profile with Class as context} 
\label{tab:profile_editing_3}
\end{table}

>>>>

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{alltt}
pathT=`Rscript -e 'cat(system.file("exec/tokenize", package="qlcData"))'`
pathW=`Rscript -e 'cat(system.file("exec/writeprofile", package="qlcData"))'`
\end{alltt}
\end{kframe}
\end{knitrout}

Then you can make softlinks to the R executables in \texttt{/usr/local/bin} by using the following command in the terminal:

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{alltt}
sudo ln -is $pathT $pathW /usr/local/bin
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{# link executables from within R}
\hlkwd{file.symlink}\hlstd{(}\hlkwd{system.file}\hlstd{(}\hlstr{"exec/tokenize"}\hlstd{,} \hlkwc{package}\hlstd{=}\hlstr{"qlcData"}\hlstd{),} \hlstr{"/usr/local/bin"}\hlstd{)}
\hlkwd{file.symlink}\hlstd{(}\hlkwd{system.file}\hlstd{(}\hlstr{"exec/writeprofile"}\hlstd{,} \hlkwc{package}\hlstd{=}\hlstr{"qlcData"}\hlstd{),} \hlstr{"/usr/local/bin"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{( test} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{'AABB'}\hlstd{,} \hlstr{'\textbackslash{}u0041\textbackslash{}u0410\textbackslash{}u0042\textbackslash{}u0412'}\hlstd{) )}
\end{alltt}
\begin{verbatim}
## [1] "AABB" "AАBВ"
\end{verbatim}
\begin{alltt}
\hlkwd{write.profile}\hlstd{(test)}
\end{alltt}
\begin{verbatim}
##   Grapheme Frequency Codepoint                UnicodeName
## 1        A         3    U+0041     LATIN CAPITAL LETTER A
## 2        B         3    U+0042     LATIN CAPITAL LETTER B
## 3        А         1    U+0410  CYRILLIC CAPITAL LETTER A
## 4        В         1    U+0412 CYRILLIC CAPITAL LETTER VE
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{example} \hlkwb{<-} \hlstr{'\textbackslash{}u00d9\textbackslash{}u00da\textbackslash{}u00db\textbackslash{}u0055\textbackslash{}u0300\textbackslash{}u0055\textbackslash{}u0301\textbackslash{}u0055\textbackslash{}u0302'}
\hlstd{profile_1} \hlkwb{<-} \hlkwd{write.profile}\hlstd{(example)}
\end{alltt}
\end{kframe}
\end{knitrout}

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Gr. & Freq. & Codepoint & Unicode Name \\ 
  \midrule
Ú & 1 & U+00DA & LATIN CAPITAL LETTER U WITH ACUTE \\ 
  Ú & 1 & U+0055, U+0301 & LATIN CAPITAL LETTER U, COMBINING ACUTE ACCENT \\ 
  Ù & 1 & U+00D9 & LATIN CAPITAL LETTER U WITH GRAVE \\ 
  Ù & 1 & U+0055, U+0300 & LATIN CAPITAL LETTER U, COMBINING GRAVE ACCENT \\ 
  Û & 1 & U+00DB & LATIN CAPITAL LETTER U WITH CIRCUMFLEX \\ 
  Û & 1 & U+0055, U+0302 & LATIN CAPITAL LETTER U, COMBINING CIRCUMFLEX ACCENT \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 1 (default settings, splitting grapheme clusters)} 
\label{tab:profile1}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & Unicode Name \\ 
  \midrule
́ & 1 & U+0301 & COMBINING ACUTE ACCENT \\ 
  ̀ & 1 & U+0300 & COMBINING GRAVE ACCENT \\ 
  ̂ & 1 & U+0302 & COMBINING CIRCUMFLEX ACCENT \\ 
  U & 3 & U+0055 & LATIN CAPITAL LETTER U \\ 
  Ú & 1 & U+00DA & LATIN CAPITAL LETTER U WITH ACUTE \\ 
  Ù & 1 & U+00D9 & LATIN CAPITAL LETTER U WITH GRAVE \\ 
  Û & 1 & U+00DB & LATIN CAPITAL LETTER U WITH CIRCUMFLEX \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 2 (splitting by code points)} 
\label{tab:profile2}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & Unicode Name \\ 
  \midrule
Ú & 2 & U+00DA & LATIN CAPITAL LETTER U WITH ACUTE \\ 
  Ù & 2 & U+00D9 & LATIN CAPITAL LETTER U WITH GRAVE \\ 
  Û & 2 & U+00DB & LATIN CAPITAL LETTER U WITH CIRCUMFLEX \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 3 (splitting by NFC code points)} 
\label{tab:profile3}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & Unicode Name \\ 
  \midrule
́ & 2 & U+0301 & COMBINING ACUTE ACCENT \\ 
  ̀ & 2 & U+0300 & COMBINING GRAVE ACCENT \\ 
  ̂ & 2 & U+0302 & COMBINING CIRCUMFLEX ACCENT \\ 
  U & 6 & U+0055 & LATIN CAPITAL LETTER U \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 4 (splitting by NFD code points)} 
\label{tab:profile4}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Gr. & Freq. & Codepoint & Unicode Name \\ 
  \midrule
Ú & 2 & U+0055, U+0301 & LATIN CAPITAL LETTER U, COMBINING ACUTE ACCENT \\ 
  Ù & 2 & U+0055, U+0300 & LATIN CAPITAL LETTER U, COMBINING GRAVE ACCENT \\ 
  Û & 2 & U+0055, U+0302 & LATIN CAPITAL LETTER U, COMBINING CIRCUMFLEX ACCENT \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 5 (splitting by graphemes after NFD)} 
\label{tab:profile5}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[H]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Gr. & Freq. & Codepoint & Unicode Name \\ 
  \midrule
Ú & 2 & U+00DA & LATIN CAPITAL LETTER U WITH ACUTE \\ 
  Ù & 2 & U+00D9 & LATIN CAPITAL LETTER U WITH GRAVE \\ 
  Û & 2 & U+00DB & LATIN CAPITAL LETTER U WITH CIRCUMFLEX \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Profile 6 (splitting by graphemes after NFC)} 
\label{tab:profile6}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & UnicodeName \\ 
  \midrule
sh &  &  &  \\ 
  ch &  &  &  \\ 
  sch &  &  &  \\ 
  ie &  &  &  \\ 
  oo &  &  &  \\ 
  a & 2 & U+0061 & LATIN SMALL LETTER A \\ 
  c & 2 & U+0063 & LATIN SMALL LETTER C \\ 
  e & 3 & U+0065 & LATIN SMALL LETTER E \\ 
  f & 1 & U+0066 & LATIN SMALL LETTER F \\ 
  h & 4 & U+0068 & LATIN SMALL LETTER H \\ 
  i & 3 & U+0069 & LATIN SMALL LETTER I \\ 
  m & 4 & U+006D & LATIN SMALL LETTER M \\ 
  o & 2 & U+006F & LATIN SMALL LETTER O \\ 
  p & 2 & U+0070 & LATIN SMALL LETTER P \\ 
  s & 4 & U+0073 & LATIN SMALL LETTER S \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Manually edited profile skeleton} 
\label{tab:profile_skeleton1}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{lllll}
  \toprule
Left & Grapheme & Frequency & Codepoint & UnicodeName \\ 
  \midrule
mi & s &  &  &  \\ 
   & sh &  &  &  \\ 
   & ch &  &  &  \\ 
   & sch &  &  &  \\ 
   & ie &  &  &  \\ 
   & oo &  &  &  \\ 
   & a & 2 & U+0061 & LATIN SMALL LETTER A \\ 
   & c & 2 & U+0063 & LATIN SMALL LETTER C \\ 
   & e & 3 & U+0065 & LATIN SMALL LETTER E \\ 
   & f & 1 & U+0066 & LATIN SMALL LETTER F \\ 
   & h & 4 & U+0068 & LATIN SMALL LETTER H \\ 
   & i & 3 & U+0069 & LATIN SMALL LETTER I \\ 
   & m & 4 & U+006D & LATIN SMALL LETTER M \\ 
   & o & 2 & U+006F & LATIN SMALL LETTER O \\ 
   & p & 2 & U+0070 & LATIN SMALL LETTER P \\ 
   & s & 4 & U+0073 & LATIN SMALL LETTER S \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Orthography profile with contextual specification for <s>} 
\label{tab:profile_skeleton2}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{lllll}
  \toprule
Left & Grapheme & Right & Class & Replacement \\ 
  \midrule
 & a &  &  & a \\ 
   & c &  &  & c \\ 
   & e &  &  & e \\ 
   & i &  &  & i \\ 
   & n &  &  & n \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Orthography profile with empty columns for editing contexts} 
\label{tab:profile_editing_1}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{lllll}
  \toprule
Left & Grapheme & Right & Class & IPA \\ 
  \midrule
 & c & [ie] &  & tʃ \\ 
   & a &  &  & a \\ 
   & n &  &  & n \\ 
   & c &  &  & k \\ 
   & e &  &  & e \\ 
   & i &  &  & i \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Orthography profile with regex as context} 
\label{tab:profile_editing_2}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Aug  9 20:07:08 2018
\begin{table}[htb]
\centering
\begingroup\scriptsize
\begin{tabular}{lllll}
  \toprule
Left & Grapheme & Right & Class & IPA \\ 
  \midrule
 & c & Vfront &  & tʃ \\ 
   & a &  &  & a \\ 
   & n &  &  & n \\ 
   & c &  &  & k \\ 
   & e &  & Vfront & e \\ 
   & i &  & Vfront & i \\ 
   \bottomrule
\end{tabular}
\endgroup
\caption{Orthography profile with Class as context} 
\label{tab:profile_editing_3}
\end{table}
